Supplemental material

### 2024-08-29 supplemental_material.Rmd
suuplemental matieral figures

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

## Packages

```{r}
if(!require(here)) install.packages("here")
library(here)

if(!require(ggplot2)) install.packages("ggplot2")
library(ggplot2)

if(!require(dplyr)) install.packages("dplyr")
library(dplyr)

if(!require(tidyr)) install.packages("tidyr")
library(tidyr)

if(!require(viridis)) install.packages("viridis")
library(viridis)

if(!require(gridExtra)) install.packages("gridExtra")
library(gridExtra)

if(!require(readr)) install.packages("readr")
library(readr)

if(!require(plyr)) install.packages("plyr")
library(plyr)

if(!require(stringr)) install.packages("stringr")
library(stringr)

if(!require(readxl)) install.packages("readxl")
library(readxl)

if(!require(data.table)) install.packages("data.table")
library(data.table)

if(!require(xfun)) install.packages("xfun")
library(xfun)

if(!require(cowplot)) install.packages("cowplot")
library(cowplot)

if(!require(gganimate)) install.packages("gganimate")
library(gganimate)

if(!require(ggExtra)) install.packages("ggExtra")
library(ggExtra)

if(!require(plotly)) install.packages("plotly")
library(plotly)

if(!require(brms)) install.packages("brms")
library(brms)

if(!require(bayestestR)) install.packages("bayestestR")
library(bayestestR)

if(!require(emmeans)) install.packages("emmeans")
library(emmeans)

if(!require(ROSE)) install.packages("ROSE")
library(ROSE)

if(!require(Rmisc)) install.packages("Rmisc")
library(Rmisc)

if(!require(metafolio)) install.packages("metafolio")
library(metafolio)

if(!require(tibble)) install.packages("tibble")
library(tibble)

if(!require(modelr)) install.packages("modelr")
library(modelr)

if(!require(tidybayes)) install.packages("tidybayes")
library(tidybayes)

if(!require(mgcv)) install.packages("mgcv")
library(mgcv)

if(!require(ciTools)) install.packages("ciTools")
library(ciTools)

if(!require(gratia)) install.packages("gratia")
library(gratia)

if(!require(scales)) install.packages("scales")
library(scales)

if(!require(patchwork)) install.packages("patchwork")
library(patchwork)

if(!require(ggforce)) install.packages("ggforce")
library(ggforce)
```

# Load vehicle data

This provides timing responses to takeovers and collision data. We also remove participants that were removed in the gaze entropy analysis.

```{r}
# response data frame for vehicle and eye data per trial
response.vehicle.eye <- fread(file = here::here("takeover_performance_cogload_time_budget/Data/takeover.responses.critical.lat.long.csv"))

# removing participants from vehicle and gaze data
response.vehicle.eye <- response.vehicle.eye %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  tidyr::drop_na()

# make collision data 1s and 0s
response.vehicle.eye <- response.vehicle.eye %>%
  dplyr::mutate(collision = case_when(collision == TRUE ~ 1,
                                      collision == FALSE ~ 0))

# computing outliers for braking reaction time
response.vehicle.eye <-  response.vehicle.eye %>%
  #dplyr::filter(collision == 0) %>%
  tidyr::drop_na() %>%
  dplyr::group_by(n_back, ttc_criticality.x) %>%
  dplyr::mutate(mean.rt = mean(rt), sd.rt = sd(rt)) %>%
  dplyr::mutate(sd.rt.4 =  sd.rt * 4) %>%
  dplyr::mutate(mean_4_sd = mean.rt + sd.rt.4) %>%
  dplyr::mutate(rt.outlier = rt > mean_4_sd)

# calculating outliers for hands on reaction time
response.vehicle.eye <-  response.vehicle.eye %>%
  #dplyr::filter(collision == 0) %>%
  tidyr::drop_na() %>%
  dplyr::group_by(n_back, ttc_criticality.x) %>%
  dplyr::mutate(mean.ho = mean(ho.rt), sd.ho = sd(ho.rt)) %>%
  dplyr::mutate(sd.ho.4 =  sd.ho * 4) %>%
  dplyr::mutate(mean_4_sd = mean.ho + sd.ho.4) %>%
  dplyr::mutate(ho.outlier = ho.rt > mean_4_sd)

# removing outliers
response.vehicle.eye <- response.vehicle.eye %>%
  dplyr::filter(rt.outlier == FALSE, ho.outlier == FALSE, ho.rt != 0, collision == 0, ho.rt > .15) %>%
  dplyr::mutate(ttc_criticality_factor = as.factor(ttc_criticality.x))
```

## Braking reaction time

```{r}
# loading model
braking_rt_shifted_lognormal_maximal <- readRDS(here::here("takeover_performance_cogload_time_budget/Models/braking_rt_shifted_lognormal_maximal.rds"))

# posterior predictive checks
brt_stat_grouped_ttc <- pp_check(braking_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "ttc_criticality_factor")
brt_stat_grouped_nback <- pp_check(braking_rt_shifted_lognormal_maximal, type = "stat_grouped", stat = "mean", group = "n_back")

# predicted global mean RTs implied by the model # setting re_formula = NA tells the function to not use any random effects - here we plot the TTC specific distributions 
predicted_braking_rt_ttc <- braking_rt_shifted_lognormal_maximal %>% 
  epred_draws(newdata = expand_grid(ttc_criticality_factor = c(as.factor(3), as.factor(5)),
                                    n_back = FALSE),
              re_formula = NA)

predicted_braking_rt_ttc %>% mean_hdi()

ttc_labs <- c("TTC = 3 s", "TTC = 5 s")
names(ttc_labs) <- c(as.factor(3), as.factor(5))

### STAT GROUPED PLOTS FOR MEAN BRT

# mean BRT for critcality
sm_fig_1_1 <- ggplot(brt_stat_grouped_ttc[["data"]] %>%
         dplyr::mutate(ttc_criticality_factor = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(ttc_criticality_factor) %>%
               dplyr::summarise(mean_brt = mean(rt)), mapping = aes(xintercept = mean_brt, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(1.0, 1.5), breaks = seq(1.0, 1.4, .1), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.593, .65), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

n_back_labs <- c("No N-back", "N-back")
names(n_back_labs) <- c(FALSE, TRUE)

# mean BRT for N-back
sm_fig_1_2 <- ggplot(brt_stat_grouped_nback[["data"]] %>%
         dplyr::mutate(n_back = as.factor(group)), mapping = aes(value)) +
  geom_histogram(aes(fill = "T(y_rep)"),col = "black") + 
  geom_vline(response.vehicle.eye %>% 
               dplyr::group_by(n_back) %>%
               dplyr::summarise(mean_brt = mean(rt)), mapping = aes(xintercept = mean_brt, fill = "T(y)"), col = "darkblue", size = 2) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  scale_fill_manual(name = "T = mean", values = c("darkblue", "lightblue"), labels = c(expression(T(y)), expression(T(y[rep])))) +
  scale_x_continuous(limits = c(1.0, 1.5), breaks = seq(1.0, 1.4, .1), labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig1 <- sm_fig_1_1 / sm_fig_1_2

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig1.tiff"), plot = sm_fig1, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

### DENSITY POSTERIOR PLOTS

pp_check(braking_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "n_back", ndraws = 100) 
pp_check(braking_rt_shifted_lognormal_maximal, type = "dens_overlay_grouped", group = "ttc_criticality_factor", ndraws = 100)

yrep_brt <- response.vehicle.eye %>% 
  select(rt, n_back, ttc_criticality_factor, ppid) %>% 
  add_predicted_draws(braking_rt_shifted_lognormal_maximal, ndraws = 100)

sm_fig2_1 <- ggplot() + 
  geom_density(yrep_brt, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ ttc_criticality_factor, labeller = labeller(ttc_criticality_factor = ttc_labs)) +
  xlim(0, 5) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("A") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = c(.94, .69), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig2_2 <- ggplot() + 
  geom_density(yrep_brt, mapping = aes(.prediction, group = .draw, col = "y_rep"), alpha = .8) +
  geom_density(response.vehicle.eye, mapping = aes(rt, col = "y"), size = 1) +
  scale_colour_manual(name = " ", values = c("darkblue", "lightblue"), labels = c(expression(y), expression(y[rep]))) +
  facet_wrap(~ n_back, labeller = labeller(n_back = n_back_labs)) +
  xlim(0, 5) +
  scale_y_continuous(expand = c(0, 0)) +
  ggtitle("B") +
  ylab(" ") +
  xlab(expression(RT[B]~ "(s)")) +
  theme_bw() +
  theme(legend.position = "none", axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), title = element_text(size = 18), legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 15, face = "bold"), strip.text = element_text(face = "bold", size = 10))

sm_fig2 <- sm_fig2_1 / sm_fig2_2

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Supplemental material/Figures/sm_fig2.tiff"), plot = sm_fig2, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

### SIMULATED NEW PARTICIPANTS

# - change NA to observed data - then use legend to identify y versus y_rep
brt_hist <- pp_check(braking_rt_shifted_lognormal_maximal, type = "hist", ndraws = 11)

ggplot(brt_hist[["data"]], mapping = aes(value)) +
  geom_histogram() +
  facet_wrap(~ rep_id)
```
